Hidden Talents Multiverse Analysis

### 2021-06-28 README.Rmd
another attempt
revert  README.Rmd back to a github_document output
trying, again :(
testing something out

cat(
  "|script|input|output|",
  "|------|-----|------|",
  glue::glue_data(
    data_prep,
    "|{script}|{input}|{output}|"
  ),
  sep = "\n "
)
```

>>>>

cat(
  "|script|input|output|",
  "|------|-----|------|",
  glue::glue_data(
    data_prep,
    "|{script}|{input}|{output}|"
  ),
  sep = "\n"
)
```

|script|input|output|
|------|-----|------|
|1-data-non-abritrary.R|data1_raw.Rdata|1-raw.csv<br> 2-non_arbitrary.csv<br> 3-composites.csv<br> 4-multiverse_base.csv<br> vars1_raw.csv<br> vars2_non_arbitrary.csv<br> vars3_composites.csv<br> vars4_multiverse_base.csv<br> data2_analysis.Rdata|
|2-primary-multiverse-datasets.R|data2_analysis.Rdata|datalist-agg-ivs.Rdata|
|3-secondary-multiverse-datasets.R|data2_analysis.Rdata|datalist-all-ivs.Rdata|
